MP MetaAnalysis

### 2018-07-05 Paper_Analyses.Rmd
fleshing out analyses for paper

@@

@@

@@

@@

```{r MPEffect}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

@@

rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)

summary(rma_MPeffect_1)

@@

@@

@@

@@

summary(rma_MP_age)
```

@@

```{r MPEffect_age}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

@@

@@

## Plotting Mispronunciation Effect

@@

### Plot Mispronunciation Effect by Age (bw)

```{r PlotMPEffect_BW}

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape=condition_label, color=condition_label),
             show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_color_grey()+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_BW.jpg", p,height= 3,width= 6)

@@

Hedges' g was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

@@

@@

Hedges' g was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

@@

Number of features is still significant

@@

## Plotting number of Features Changed

@@

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

summary(rma_Distractor)

@@

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

Hedges' g was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

### Plotting Distractor Familiarity

### Plot Distractor Familiarity

### Plot Distractor Familiarity

### Plot Distractor Familiarity by age (subset to same age range)

```{r PlotDistFamEffect_age}

dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")
dat$dist_code <- ifelse(dat$object_pair == "familiar_familiar", "familiar", "unfamiliar")

p <- ggplot(dat_age, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = dist_code),show.legend=FALSE) + 
  facet_grid(.~dist_code)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_color_manual(values=cbPalette)+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

  jpeg(filename = "figures/Distractor_fam_AgeSubset.jpg", 
       width = 500, height = 300, units = "px")

@@

summary(rma_Location)

@@

@@

summary(rma_LocationAge)
```

@@

@@

summary(rma_LocationCondition)
```

@@

summary(rma_LocationCondition)
```

@@

p <- ggplot(dat.p, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = mispron_location),show.legend=FALSE) + 
  facet_grid(.~mispron_location)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_position.jpg", p)

@@

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)

@@

@@

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)

@@

@@

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)

@@

@@

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)

@@

@@

## Plotting Distractor Overlap

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = distractor_overlap),show.legend=FALSE) + 
  facet_grid(.~distractor_overlap)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_distractor_overlap.jpg", p)

```{r LanguageEffectAnalyses}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

```{r LanguageEffectAnalyses_age}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

```{r LanguageEffectAnalyses_condition}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~condition*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

```{r LanguageEffectAnalyses_condition_age}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="Danish" | dat$native_lang=="Swedish" |
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

## Plotting Language Effect
```{r PlotLanguageEffect}

dat$lang_family = ifelse(dat$native_lang=="American English" | dat$native_lang=="British English" |
                           dat$native_lang=="Dutch" | dat$native_lang=="English" | 
                           dat$native_lang=="German", "Germanic",
                         ifelse(dat$native_lang == "French" | dat$native_lang == "Catalan" |
                                  dat$native_lang == "Spanish" | dat$native_lang == "Catalan-Spanish" |
                                  dat$native_lang == "Swiss French", "Romanic", "Sino-Tibetian"))

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g, shape = lang_family),show.legend=FALSE) + 
  facet_grid(.~lang_family)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

ggsave("figures/AgeEffect_log_language.jpg", p)

@@

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

@@

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

Hedges' g was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

## Plotting MP type: Consonant, Vowel, or Tone?

@@

@@

>>>>

#aov.type <- anova(rma_correct)

sum_eff <- round(coef(summary(rma_correct))[1,], 2)

@@

Correct pronunciations were significantly greater than 0:

Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

sum_eff <- round(coef(summary(rma_MP))[1,], 2)

@@

Mispronunciations were significantly greater than 0:

Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

```{r MPEffect}

@@

#rma_MPeffect_1 <- rma.mv(g_calc, g_var_calc, mods = ~condition-1, data = dat, random = ~ collapse | short_cite)

#summary(rma_MPeffect_1)

aov.type <- anova(rma_MPeffect)

sum_eff <- round(coef(summary(rma_MPeffect))[2,], 2)

@@

There was a significant effect of condition:

Hedges' g for `rownames(sum_eff)`  was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

@@

aov.type <- anova(rma_correct_age)

sum_eff <- round(coef(summary(rma_correct_age))[2,], 2)

@@

The moderator test was not significant:
`print(aov.feat)`

There was no significant effect of age:

Hedges' g for `rownames(sum_eff)`  was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

@@

summary(rma_MP_age)

aov.type <- anova(rma_MP_age)

sum_eff <- round(coef(summary(rma_MP_age))[2,], 2)

The moderator test was not significant:
`print(aov.feat)`

There was no significant effect of age:

Hedges' g for `rownames(sum_eff)`  was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

@@

```{r MPEffect_age}

@@

aov.type <- anova(rma_MPeffect_age)

sum_eff <- round(coef(summary(rma_MPeffect_age))[4,], 2)

@@

There was no significant interaction between condition and age:

Hedges' g for `rownames(sum_eff)`  was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

@@

@@

There was a significant effect of number of features changed:

Hedges' g for `rownames(n_feat)` was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

@@

#summary(rma_NFeatures)
aov.feat <- anova(rma_NFeatures)

@@

Hedges' g for `rownames(n_feat)` was `toString(n_feat$estimate)` (SE = `toString(n_feat$se`)
(95% CI [`toString(n_feat$ci.lb)`, `toString(n_feat$ci.ub)`], p = `toString(n_feat$pval)`)

@@

@@

@@

Hedges' g for `rownames(sum_eff)` was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

@@

Hedges' g for `rownames(sum_eff)` was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

### Plot Distractor familiarity and condition

@@

Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

### Plot Distractor Familiarity with condition, subset to same age range

@@

Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

#summary(rma_Location)

aov.type <- anova(rma_Location)

sum_eff <- round(coef(summary(rma_Location))[2,], 2)

@@

There was no significant effect of mispronunciation position:

Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

#summary(rma_LocationAge)

aov.type <- anova(rma_LocationAge)

sum_eff <- round(coef(summary(rma_LocationAge))[2,], 2)

There was no significant interaction between mispronunciation position and condition:

Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

db_ET_MPl = dat %>%
  filter(mispron_location == "onset"  | mispron_location == "medial")

@@

#summary(rma_LocationCondition)

aov.type <- anova(rma_LocationCondition)

sum_eff <- round(coef(summary(rma_LocationCondition))[4,], 2)

But there was no significant interaction between mispronunciation position and condition:

Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

summary(rma_LocationCondition)

aov.type <- anova(rma_LocationCondition)

sum_eff <- round(coef(summary(rma_LocationCondition))[8,], 2)

But there was no significant interaction between mispronunciation position, condition, and age:

Hedges' g for `rownames(sum_eff)`  was `toString(sum_eff$estimate)` (SE = `toString(sum_eff$se`)
(95% CI [`toString(sum_eff$ci.lb)`, `toString(sum_eff$ci.ub)`], p = `toString(sum_eff$pval)`)

@@

p <- ggplot(dat.p, aes(condition_label, g_calc, fill = condition_label)) + 
  facet_grid(.~mispron_location)+
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Mispronunciation_position.jpg", 
       width = 500, height = 300, units = "px")

@@

db_ET_MPo = db_ET_MP %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)

#summary(rma_DistractorOverlap)

aov.type <- anova(rma_DistractorOverlap)

sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[2,], 2)
sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[3,], 2)

@@

There was no significant effect of distractor overlap:

Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)

Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)

@@

db_ET_MPo = db_ET_MP %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)

#summary(rma_DistractorOverlap)  
aov.type <- anova(rma_DistractorOverlap)

sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[5,], 2)
sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[6,], 2)

@@

There was no significant interaction between distractor overlap and age:

Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)

Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)

@@

db_ET_MPo = dat %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)

@@

aov.type <- anova(rma_DistractorOverlap)

sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[5,], 2)
sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[6,], 2)

There was a significant interaction between distractor overlap and condition:

Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)

Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)

### Plotting Distractor Overlap with condition

db_ET_MPo = dat %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

p <- ggplot(db_ET_MPo, aes(condition_label, g_calc, fill = condition_label)) + 
  facet_grid(.~distractor_overlap)+
  geom_boxplot() + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Distractor_overlap.jpg", 
       width = 500, height = 300, units = "px")

@@

db_ET_MPo = dat %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MPo, random = ~ collapse | short_cite)

@@

aov.type <- anova(rma_DistractorOverlap)

sum_eff1 <- round(coef(summary(rma_DistractorOverlap))[11,], 2)
sum_eff2 <- round(coef(summary(rma_DistractorOverlap))[12,], 2)

@@

There was a significant interaction between distractor overlap, condition, and age:

Hedges' g for `row.names(sum_eff1)` was `toString(sum_eff1$estimate)` (SE = `toString(sum_eff1$se`)
(95% CI [`toString(sum_eff1$ci.lb)`, `toString(sum_eff1$ci.ub)`], p = `toString(sum_eff1$pval)`)

Hedges' g `row.names(sum_eff2)` was `toString(sum_eff2$estimate)` (SE = `toString(sum_eff2$se`)
(95% CI [`toString(sum_eff2$ci.lb)`, `toString(sum_eff2$ci.ub)`], p = `toString(sum_eff2$pval)`)

### Plot Distractor Overlap, condition, and age

db_ET_MPo = dat %>%
  filter(distractor_overlap == "onset"  | distractor_overlap == "novel" | distractor_overlap == "no")

p <- ggplot(db_ET_MPo, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
    facet_grid(.~distractor_overlap)+
  geom_point(aes(size = weights_g),show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Distractor_overlap_age.jpg", 
       width = 500, height = 300, units = "px")

@@

Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

@@

Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

@@

Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

@@

```{r LanguageEffectAnalyses}

dat_lang <- subset(db_ET_MP, lang_family != "Sino-Tibetian")

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~lang_family, data = dat_lang, random = ~ collapse | short_cite)
#summary(rma_lang_interaction)

aov.type <- anova(rma_lang_interaction)

type_feat <- round(coef(summary(rma_lang_interaction))[2,], 2)

There was no significant effect of language family:

Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

```{r LanguageEffectAnalyses_age}

dat_lang <- subset(db_ET_MP, lang_family != "Sino-Tibetian")

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*lang_family, data = dat_lang, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

aov.type <- anova(rma_lang_interaction)

type_feat <- round(coef(summary(rma_lang_interaction))[4,], 2)

There was a significant interaction between language family and age:

Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

### Plot Language effect with age

```{r PlotLanguageEffect}

dat_lang <- subset(dat, lang_family != "Sino-Tibetian")

p <- ggplot(dat_lang, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
    facet_grid(.~lang_family)+
  geom_point(aes(size = weights_g),show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")

  jpeg(filename = "figures/Language_Age.jpg", 
       width = 500, height = 300, units = "px")

  dev.off()
```

```{r LanguageEffectAnalyses_condition}

dat_lang <- subset(dat, lang_family != "Sino-Tibetian")

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~condition*lang_family, data = dat_lang, random = ~ collapse | short_cite)
#summary(rma_lang_interaction)

aov.type <- anova(rma_lang_interaction)

type_feat <- round(coef(summary(rma_lang_interaction))[4,], 2)

But, there was no significant interaction between language family and condition:

Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)

```{r LanguageEffectAnalyses_condition_age}

dat_lang <- subset(dat, lang_family != "Sino-Tibetian")

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat_lang, random = ~ collapse | short_cite)
#summary(rma_lang_interaction)

aov.type <- anova(rma_lang_interaction)

type_feat <- round(coef(summary(rma_lang_interaction))[8,], 2)

But, there was no significant interaction between language family, age, and condition:

Hedges' g for `rownames(sum_eff)`  was `toString(type_feat$estimate)` (SE = `toString(type_feat$se`)
(95% CI [`toString(type_feat$ci.lb)`, `toString(type_feat$ci.ub)`], p = `toString(type_feat$pval)`)
